Boutiques: a flexible framework for automated application integration in computing platforms

### 2016-12-08 paper.tex
Fixes @johnflavin's comment in #1

\author{Tristan Glatard, Tristan Aumentado-Armstrong, Natacha Beck, Pierre Bellec,\\
        Remi Bernard, Sorina Camarasu-Pop, Fr\'ed\'eric Cervenansky, Samir Das, \\
        Rafael Ferreira da Silva, Guillaume Flandin, John Flavin, Pascal Girard, \\
         Krzysztof J. Gorgolewski, Charles G. Guttmann, Nathaniel Kofalt, Pierre-Olivier Quirion,\\
         Pierre Rioux, Gunnar Schaeffer, Marc-\'Etienne Rousseau, Alan C. Evans}

@@

>>>>

\author{Tristan Glatard, Tristan Aumentado-Armstrong, Natacha Beck, Pierre Bellec,\\
        Remi Bernard, Sorina Camarasu-Pop, Fr\'ed\'eric Cervenansky, Samir Das, \\
        Rafael Ferreira da Silva, Guillaume Flandin, John Flavin, Pascal Girard, \\
         Krzysztof J. Gorgolewski, Charles G. Guttmann, Nathaniel Kofalt, Pierre-Olivier Quirion,\\
         Pierre Rioux, Marc-\'Etienne Rousseau, Gunnar Schaeffer, Alan C. Evans}

@@

\subsection{Reproducibility}

\boutiques helps reproduce\footnote{in Peng's
  sense~\cite{peng2011reproducible}} executions through containers and
formal command-line descriptions. With \boutiques, complete sets of
applications could be easily migrated across execution platforms,
including high-performance computing platforms and individual laptops,
to reproduce analyses. The \boutiques manifest describes the
parameters and implementation of the application, and the invocation
schema describes the parameter values.

However, reproducibility is a large problem that \boutiques only
partially addresses. At the command-line execution level, containers
help freeze a large fraction of the software ecosystem but they do not
shield against discrepancies arising from different Linux kernel
versions or hardware platforms. For instance, containers may not
execute consistently on different x86\_64 CPUs (e.g. Intel and AMD)
when software compiled with architecture-specific flags is involved
(see for instance GCC's \texttt{-march} flag).

In addition, important runtime parameters, for instance related to
multi-threading or available resources (storage, RAM), may be set by
the execution platform without being specified in the \boutiques
manifest. Such runtime parameters may impact reproducibility in some
cases. To properly cover this issue, \boutiques manifests should be
complemented by a provenance framework that captures a detailed trace
of the execution.

At a higher level, reproducibility is impacted by factors
such as data sharing~\cite{poldrack2014making} which are out of the
scope of \boutiques.
